\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-23 concepts.tex
updates to reviews

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{figs/flexible-timelines.pdf}
\caption{\small Tokens with flexible temporal intervals and parametric
  constraints between tokens. This example shows the triggering of a
  water sampler based on a feature threshold while the vehicle
  Yo-Yo's. The \texttt{Waypoint\_Yo-Yo} token has a flexible duration,
  start \& end times.}
\label{fig:flex-timelines}
\end{figure}

@@

  In general, for an executable plan it is insufficient to state
  predicates that describe required state or behavior without also
  specifying some temporal extent over which each of those predicates
  hold. Predicates that are always true can be thought to hold from
  the beginning to the end of the planning horizon. However, in
  practice, the temporal extent of interest must be defined with
  timepoints \cite{Dean88} to represent its start and end.  In such
  representation, one writes \texttt{At($a$,$s$,$e$,$l$)} to indicate
  that agent $a$ is at location $l$ from time $s$ to time $e$. In
  fact, this pattern of using such predicates to describe both state
  and behavior of objects is prevalent enough that \eu the token
  representation. Token have built in variables to indicate the object
  to which the statement principally applies as well as the timepoints
  over which it holds. A token is an instance of a predicate that
  represents an object's state or behavior and is defined over a
  temporal extent. In \eu, all predicate instances are tokens. Also,
  in the same way that objects are described generically by classes,
  in \eu tokens can be described generically by token types. Every
  token has five built-in variables:

@@

  \begin{figure} \centering
    \includegraphics[scale=0.4]{figs/europa-pr-1.pdf}
    \caption{\small Timelines representing initial state and goals for a Shopping Agent.}
    \label{fig:europapr1}
  \end{figure}

  Note that the tokens \texttt{Own(Drill)} and \texttt{At(Home)} that
  represent the goals are not immediately placed on the
  \texttt{AgentBag} or \texttt{AgentLocation} timelines since \eu must
  first determine whether it can achieve those goal and how. When the
  goals are posted and before any decisions are made, the
  \texttt{Own(Drill)} and \texttt{At(Home)} tokens are created in an
  \texttt{INACTIVE} state. \eu then considers the partial plan and
  evaluates two possible alternatives:

@@

When a token is merged, all restrictions imposed on the merged token
are transferred to the active token upon which it is merged. Merging a
token requires finding a target active token that is compatible. Two
tokens are merge-compatible if they are instances of the same
predicate and there are no empty intersections between corresponding
token variables.  The effect of merging is illustrated in
Fig. \ref{fig:europapr:merge}

\begin{figure} 
  \centering
  \includegraphics[scale=0.4]{figs/europa-pr-merge.pdf}
  \caption{\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial state.}
  \label{fig:europapr:merge}
\end{figure}

The goal to be home by time $20$ is satisfied by merging with the
initial state that said that the Agent is home at time $0$.  The merge
is possible because the tokens are of the same type \texttt{At}, and
intersecting the domains for all of their variables doesn't yield an
empty domain (which represents an inconsistency), in this case the
token variables are the location, which is \texttt{Home} in both
cases, and the temporal variables (start, end, duration), which can be
intersected without causing an inconsistency. After the token
representing the goal is merged onto the token representing the
initial state, the resulting token represents not only the fact that
the Agent must be \texttt{At(Home)} by time 0 but also
\texttt{At(Home)} at time $20$, this is reflected in the new
constraints on the token's start and end variables as depicted in
Fig. \ref{fig:europapr:merge}.

When a token is activated, all domain rules associated with its type
are evaluated, which may lead to new subgoals being generated. In our
example, there could be a domain rule stating that if a Shopping Agent
doesn't already own a product, then it must \texttt{Buy} it before it
can \texttt{Own} it. In such a case, activating the
\texttt{Own(Drill)} token will cause a new \texttt{Buy(Drill)} to be
created in an \texttt{INACTIVE} state, which in turn could spawn its
own subgoals, like being at the location where the product can be
purchased before being able to buy it, and so on, until all domain
rules are satisfied.

\begin{figure} \centering
  \includegraphics[scale=0.4]{figs/europa-pr-activate.pdf}
  \caption{\small State of timelines after satisfying a goal to own a
    drill by time $10$ by activating corresponding token.}
\label{fig:europapr:activate}
\end{figure}

As Fig. \ref{fig:europapr:activate} shows the decision to merge the
goal to be \texttt{At(Home)} by time $20$ with the initial state was
not appropriate since the Agent will have to get away from
\texttt{Home} to be able to buy the drill which is inconsistent with
the constraints that resulted after the merge. As a result that
decision will have to be retracted at some point and the alternative
to activate or merge with a different token will have to be
considered.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{figs/flexible-timelines.pdf}
\caption{\small Tokens with flexible temporal intervals and parametric
  constraints between tokens. This example shows the triggering of a
  water sampler based on a feature threshold while the vehicle
  Yo-Yo's. The \texttt{Waypoint\_Yo-Yo} token has a flexible duration,
  start \& end times.}
\label{fig:flex-timelines}
\end{figure}

@@

  In general, for an executable plan it is insufficient to state
  predicates that describe required state or behavior without also
  specifying some temporal extent over which each of those predicates
  hold. Predicates that are always true can be thought to hold from
  the beginning to the end of the planning horizon. However, in
  practice, the temporal extent of interest must be defined with
  timepoints \cite{Dean88} to represent its start and end.  In such
  \kcomment{a} representation, one writes \texttt{At($a$,$s$,$e$,$l$)}
  to indicate that agent $a$ is at location $l$ from time $s$ to time
  $e$. In fact, this pattern of \kcomment{usage} to describe both
  state and behavior of objects is prevalent enough that \eu
  \kcomment{encapsulates into} the token
  representation. \kcomment{Tokens} have built in variables to
  indicate the object to which \kcomment{it primarily} applies as well
  as the timepoints over which it holds. A token, therefore, is an
  instance of a predicate that represents an object's state or
  behavior and is defined over a temporal extent. In \eu, all
  predicate instances are tokens. \kcomment{In} the same way that
  objects are described generically by classes, in \eu tokens can be
  described generically by token types. Every token has five built-in
  variables:

@@

  \begin{figure}[t]
    \centering 
    \subfloat[\small Timelines representing initial state
    and goals for a Shopping Agent.]{\label{fig:europapr1}\includegraphics[scale=0.4]{figs/europa-pr-1.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial state.]{\label{fig:europapr:merge}\includegraphics[scale=0.4]{figs/europa-pr-merge.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to own
    a drill by time $10$ by activating corresponding
    token.]{\label{fig:europapr:activate}\includegraphics[scale=0.4]{figs/europa-pr-activate.pdf}} 
    \caption{\small Evolution of a timeline from the Shopping Agent example.}
  \end{figure}

  Note that the tokens \texttt{Own(Drill)} and \texttt{At(Home)} that
  represent the goals are not immediately placed on the
  \texttt{AgentBag} or \texttt{AgentLocation} timelines since \eu must
  first determine whether it can achieve those \kcomment{goals} and
  how. When the goals are posted and before any decisions are made,
  the \texttt{Own(Drill)} and \texttt{At(Home)} tokens are created in
  an \texttt{INACTIVE} state. \eu then considers the partial plan and
  evaluates two possible alternatives:

@@

When a token is merged, all restrictions imposed on the merged token
are transferred to the active token upon which it is merged. Merging a
token requires finding a target active token that is compatible. Two
tokens are merge-compatible if they are instances of the same
predicate and there are no empty intersections between corresponding
token variables.  The effect of merging is illustrated in
Fig. \ref{fig:europapr:merge}. The goal to be home by time $20$ is
satisfied by merging with the initial state that said that the Agent
is home at time $0$.  The merge is possible because the tokens are of
the same type \texttt{At}, and intersecting the domains for all of
their variables doesn't yield an empty domain (which represents an
inconsistency), in this case the token variables are the location,
which is \texttt{Home} in both cases, and the temporal variables
(start, end, duration), which can be intersected without causing an
inconsistency. After the token representing the goal is merged onto
the token representing the initial state, the resulting token
represents not only the fact that the Agent must be \texttt{At(Home)}
by time 0 but also \texttt{At(Home)} at time $20$, this is reflected
in the new constraints on the token's start and end variables as
depicted in Fig. \ref{fig:europapr:merge}.

When a token is activated, all domain rules associated with its type
are evaluated, which may lead to new subgoals being generated. In our
example, there could be a domain rule stating that if a Shopping Agent
doesn't already own a product, then it must \texttt{Buy} it before it
can \texttt{Own} it. In such a case, activating the
\texttt{Own(Drill)} token will cause a new \texttt{Buy(Drill)} to be
created in an \texttt{INACTIVE} state, which in turn could spawn its
own subgoals, like being at the location where the product can be
purchased before being able to buy it, and so on, until all domain
rules are satisfied. As Fig. \ref{fig:europapr:activate} shows the
decision to merge the goal to be \texttt{At(Home)} by time $20$ with
the initial state was not appropriate since the Agent will have to get
away from \texttt{Home} to be able to buy the drill which is
inconsistent with the constraints that resulted after the merge. As a
result that decision will have to be retracted at some point and the
alternative to activate or merge with a different token will have to
be considered.
